A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2018-05-17 paper/paper.tex
A bit more on the description

\subsection{Grid drawings: an interesting variant.}
\label{ssec:grid}

>>>>

\subsection{Grid drawings: An interesting variant.}
\label{ssec:grid}

The algorithm, as it has been described so far, does not necessarily produce grid drawings, i.e., drawings in which the vertices are at integer coordinates. However, it can be easily adjusted to produced such drawings. Recall that, at the $i$-th iteration step, our algorithm chooses uniformly at random a vertex $v_i$ from the vertex-pool and determines a set of $\rho$ candidate points $\pi_1,\ldots,\pi_\rho$. If we round these points to their closest grid points, say $\overline{\pi}_1,\ldots,\overline{\pi}_\rho$, and use them as candidates for the next position of $v_i$, then the obtained drawing will be grid, assuming that the starting drawing is grid (the latter requirement is not difficult to be achieved, e.g., by slightly adjusting the positions of the vertices of a circular layout, whose underlying circle has large radius, to be at grid points).

An alternative approach is to let our algorithm compute a (non-grid) drawing and then apply some technique to convert it to grid. Critical here is not to affect the crossing resolution too much during the conversion. Of course, if the crossing resolution of the obtained grid drawing is at least as large as the crossing resolution of the non-grid starting drawing, then we considered the computed grid drawing \emph{acceptable}. In our approach, we also accepted drawings whose crossing resolution is at least as large as the crossing resolution of the non-grid starting drawing minus an input parameter $\epsilon$, which we used as \emph{slack} for tolerating slightly worse solutions. For converting a non-grid drawing to grid, we repeated the following procedure, that is also based on randomization, until we compute an acceptable grid drawing: For each vertex of the non-grid starting drawing, chose uniformly at random one of the grid points from the so-called \emph{neighbourhood} of the vertex, and move the vertex to this point (assuming of course that there is no other vertex at this point), where the neighbourhood of a vertex was initially set to its four closest grid points. If after a number of iterations an acceptable grid drawing without vertex-vertex overlaps could not be reported, then we augmented the neighbourhood of all vertices to contain more grid points.
